\section{Evolution of Audio}

Music has an impact on every stage of life of a human being. Audio music has been growing 
with daily life styles since prehistoric times although there isn't a particular theory 
regarding whilst and wherein music originated. Historiographers state that there are six 
periods of music and each period has a specific genre of music that vastly contributed to 
the evaluation of music upto today. In the following subsections, each music period is 
briefly described.

\subsection{Medieval Period (0-1400 A.D)}

In this period, musical notations were developed which give us an understanding of how music 
sounded at that time. The monophonic and the polyphonic were the two commonly used types of 
music during this period and most of it were subjected to religion.

\subsection{Renaissance Period (1400-1600 A.D)}

Renaissance meaning “rebirth” states a period of a new era for music where creating and perceiving 
of music were rapidly changed. Music was composed according to the new idea of concerning the thoughts 
of the listener at that time. Most of the music artists could move the listeners to devotion 
by composing music for the church.

\subsection{Baroque Period (1600-1750 A.D)}

The word “baroque” means bizzare which comes from an Italian word “Barocco”. The Baroque period is 
commonly known for complex pieces and intricate harmonies and the idea of the modern orchestra was 
created with the help of opera.

\subsection{Classical Period (1750-1800 A.D.)}

The Classical period expanded from the Baroque period making music less complex. Simpler melodies 
and forms such as the sonatas were used with the usage of the piano as the primary music instrument. 
In this era turning into public concerts is considered as a milestone in the history of music.

\subsection{Romantic Period (1800 1900 A.D.)}

Music expanded from Classical period by adding expressions and feelings with the use of various musical 
instruments such as wind instruments. Melodies were more focused on gravitating drama and emotions.

\subsection{Contemporary Period (1900-Present)}

Over time music has moved on to a complete free reign. Nowadays composers  try to do new things by 
ultimate experimentation and the usage of technology.  Music has come a long way and it has a long 
way to go and we are grateful for the countless composers who have contributed to what music is today.